---
title: "ImmVar and variancePartition"
author: "Izabela Silva"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Targets must be loaded first
# Compute Canonical Correlation Analysis (CCA) between all pairs of variables returns absolute correlation value

```{r correlation matrix}
form_cca <- ~ Individual + CellType + Batch + Sex + Age
C = canCorPairs(form_cca, info)
plotCorrMatrix(C)

```

Plot correlation matrix

```{r correlation matrix}
form_cca <- ~ Individual + CellType + Batch + Sex + Age
C = canCorPairs(form_cca, info)
```

The individual column is highly correlated with all the other columns, therefore should not be take into the formula to the modeling

#Analysis using variancePartition
varPart2 is generated within _targets.R

```{r sorting matrix}
vp <- sortCols(varPart2)
```
Bar plot of variance fractions for the first 10 genes
```{r variance fractions}
plotPercentBars( vp[1:10,] )
```
Violin plot of contribution of each variable to total variance
```{r violin plots}
plotVarPart( vp )
```
#Plot expression stratified by CellType

```{r expression by cell type}

i <- which.max(varPart$Individual )
GE <- data.frame( Expression = eset.rma[i,],
                  Individual = info$CellType)

label <- paste("CellType:", format(varPart$CellType[i]*100,
                                     digits=3), "%")
main <- rownames(eset.rma)[i]
plotStratify( Expression ~ CellType, GE, colorBy=NULL,
              text=label, main=main)
````


